The Spine of American Legal Practice

### 2016-06-23 article/article.Rmd
Correct citation

[^7]: For the rise of treatises in America generally, see G. Edward White, *The Marshall Court and Cultural Change, 1815-1835* (1988) and A.W.B. Simpson, "The Rise and Fall of the Legal Treatise: Legal Principles and the Forms of Legal Literature," in *Legal Theory and Legal History: Essays on the Common Law* (1984), 273. The most instructive treatises for New York practice in the 1840s were Oliver L. Barbour, *A Treatise on the Practice of the Court of Chancery* (1844); Alexander M. Burrill, *Treatise on the Practice of the Supreme Court of the State of New York* (1846), 2 vols.; David Graham, *A Treatise on on the Practice of the Supreme Court of the State of New York* (3d. ed. 1847); David Graham, *A Treatise on the Organization and Jurisdiction of the Courts of Law and Equity in the State of New York* (1839); Claudius L. Monell, *A Treatise on the Practice of the Supreme Court of the State of New York* (1849); Joseph W. Moulton, *The Chancery Practice of the State of New York* (1829), 2 vols.; and as a general introduction to the field, the Englishman Henry John Stephen's *Treatise on the Principles of Pleading in Civil Actions* (2d. ed. 1828).

>>>>

[^7]: For the rise of treatises in America generally, see G. Edward White, *The Marshall Court and Cultural Change, 1815--1835* (1988) and A. W. B. Simpson, "The Rise and Fall of the Legal Treatise: Legal Principles and the Forms of Legal Literature," in *Legal Theory and Legal History: Essays on the Common Law* (London: Hambledon Press, 1987), 273--320. The most instructive treatises for New York practice in the 1840s were Oliver L. Barbour, *A Treatise on the Practice of the Court of Chancery* (1844); Alexander M. Burrill, *Treatise on the Practice of the Supreme Court of the State of New York* (1846), 2 vols.; David Graham, *A Treatise on on the Practice of the Supreme Court of the State of New York* (3d. ed. 1847); David Graham, *A Treatise on the Organization and Jurisdiction of the Courts of Law and Equity in the State of New York* (1839); Claudius L. Monell, *A Treatise on the Practice of the Supreme Court of the State of New York* (1849); Joseph W. Moulton, *The Chancery Practice of the State of New York* (1829), 2 vols.; and as a general introduction to the field, the Englishman Henry John Stephen's *Treatise on the Principles of Pleading in Civil Actions* (2d. ed. 1828).
